--- 
title: "Community Contribution -- mlr3 tutorial"
author: "YLingjun Zhang, Michelle Sun"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
---
```{r include=FALSE, cache=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE
)
```

# Introduction

## Background
The mlr3 (Lang et al. 2019) package and ecosystem provide a generic, object-oriented, and extensible framework for classification, regression, survival analysis, and other machine learning tasks for the R language (R Core Team 2019). This unified interface provides functionality to extend and combine existing machine learning algorithms (learners), intelligently select and tune the most appropriate technique for a specific machine learning task, and perform large-scale comparisons that enable meta-learning. Examples of this advanced functionality include hyperparameter tuning and feature selection. Parallelization of many operations is natively supported.

## Target Users
We assume that users of mlr3 have the equivalent knowledge of an introductory machine learning course and some experience in R. A background in computer science or statistics will provide a strong basis for understanding the advanced functionality described in the later chapters of this book. “An Introduction to Statistical Learning” provides a comprehensive introduction for those getting started in machine learning. mlr3 is suitable for complex projects that utilize the high degree of control as well as the highly abstracted “syntactic sugar” to mock-up specific tasks.

mlr3 provides a domain-specific language for machine learning in R. We target both practitioners who want to quickly apply machine learning algorithms and researchers who want to implement, benchmark, and compare their new methods in a structured environment.

## Development
mlr (Bischl et al. 2016) was first released to CRAN in 2013, with the core design and architecture dating back much further. Over time, the addition of many features has led to a considerably more complex design that made it harder to build, maintain, and extend than we had hoped for. With hindsight, we saw that some design and architecture choices in mlr made it difficult to support new features, in particular with respect to pipelines. Furthermore, the R ecosystem as well as helpful packages such as data.table have undergone major changes in the meantime.

Bischl, Bernd, Michel Lang, Lars Kotthoff, Julia Schiffner, Jakob Richter, Erich Studerus, Giuseppe Casalicchio, and Zachary M. Jones. 2016. “mlr: Machine Learning in R.” Journal of Machine Learning Research 17 (170): 1–5. http://jmlr.org/papers/v17/15-066.html.
It would have been nearly impossible to integrate all of these changes into the original design of mlr. Instead, we decided to start working on a reimplementation in 2018, which resulted in the first release of mlr3 on CRAN in July 2019. The new design and the integration of further and newly-developed R packages (especially R6, future, and data.table) makes mlr3 much easier to use, maintain, and in many regards more efficient compared to its predecessor mlr.


<!--chapter:end:index.Rmd-->

```{r include=FALSE, cache=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE
)
```
# Package Prepare

## Installation
We recommend installing the full universe at once:
```{r}
install.packages("mlr3verse")
```

You can also just install the base package:
```{r}
install.packages("mlr3")
```

## Package Ecosystem
mlr3 makes use of the following packages not developed by core members of the mlr3 team:

R6: Reference class objects.
data.table: Extension of R’s data.frame.
digest: Hash digests.
uuid: Unique string identifiers.
lgr: Logging facility.
mlbench: A collection of machine learning data sets.
evaluate: For capturing output, warnings, and exceptions.
future / future.apply: For parallelization.
These are core packages within the R ecosystem.

The mlr3 package itself provides the base functionality that the rest of ecosystem (mlr3verse) rely on and some fundamental building blocks for machine learning.

<!--chapter:end:installation.Rmd-->

```{r include=FALSE, cache=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE
)
```
# Cheat Sheets

## Basic Function

## Pipeline

## Hyperparameter Tuning

## Feature Selection


<!--chapter:end:cheatsheets.Rmd-->

```{r include=FALSE, cache=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE
)
```
# Sample for Classification Problems




<!--chapter:end:Classification.Rmd-->

```{r include=FALSE, cache=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE
)
```
# Sample for Regression Problems

<!--chapter:end:Regression.Rmd-->

```{r include=FALSE, cache=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE
)
```
# Appendices


<!--chapter:end:Appendices.Rmd-->

