# Sample for Regression Problems

Here we will perform and solve a classification problem using the mlr3 package.

First, we load the data and create a machine learning task.

```{r,echo = TRUE}
library(mlr3)
library(mlr3fselect)
library(mlr3viz)

my_data =read.csv("./winequality-red.csv", sep = ";")
head(my_data)

```

We create a machine learning task:

```{r,echo = TRUE}
my_task = as_task_regr(x = my_data, target = "quality")
my_task
```

Next we choose a learner to perform a regression task:

```{r,echo = TRUE}
learner = mlr_learners$get("regr.rpart")
learner
```

Since we have 1599 observations, we will split them into test/train using 2:8.

```{r,echo = TRUE}
train_set = sample(my_task$nrow, 0.8 * my_task$nrow)
test_set = setdiff(seq_len(my_task$nrow), train_set)
```

We train the model using the test set:

```{r,echo = TRUE}
learner$train(my_task, row_ids = train_set)
learner$model
```

We then predict using the test set:

```{r,echo = TRUE}
prediction = learner$predict(my_task, row_ids = test_set)
prediction$score()
```

We can select the best feature set by using mlr3fselect package and use the auto tuner:

```{r,echo = TRUE}
# auto tuner
autos = auto_fselector(
  method = "random_search",
  learner = lrn("regr.rpart"),
  resampling = rsmp("cv"),
  measure = msr("regr.mse"),
  term_evals = 10,
  batch_size = 5
)

autos$train(my_task, row_ids = train_set)
```

```{r}
autos$fselect_result
```

Here we can see that the regr.mse decreases after performing feature selection, that means it does get better after feature selection.

## Visualization

We will use mlr3viz to create some visualizations.

```{r, echo = TRUE}
autoplot(my_task)
```

Autoplot is the default plot for my task. Here it shows a boxplot for the red wine quality. We can see that the interquartile range is between 5-6 and the median is at 5.5. We also view that there are outliers.

The resample result prediction plot and the prediction plot can only compare one or two features:

```{r,echo=TRUE}
my_task1 = my_task$select(c("citric.acid","alcohol"))
rr = resample(my_task1, learner, rsmp("cv", folds = 5), store_models = TRUE)
autoplot(rr, type = "prediction")
```

```{r, echo=TRUE}
p = plot_learner_prediction(learner, my_task)
print(p)

```
